---
title: "SQL Assessment information board"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(flexdashboard)
```



# Information board

 
###  overview & contents
This is the dashboard show casing the outcome of the SQL Assessment for Welup Digital Cohort 6.

At the end of the SQL Module, the students were tested on the knowledge of SQL. 

Kudos to everyone who attempted the assessment. 


A total of 45 persons attempted the assessment, only 44 scripts were graded, as one of the scripts were unreadable. 


```{r}

#bring in file 

file <- read.csv("abcd - Sheet1.csv")


```

## A break down of the scores

```{r scores break down}

Scores_bd <- file  %>% group_by(Scores) %>% summarise(
    `no of persons` = n())


#knitr::kable(Scores_bd, format = "html")

```


# Performance Plot

```{r chart of scores}


#reorder
Scores_bd$Scores <- factor(Scores_bd$Scores, levels = Scores_bd$Scores[order(Scores_bd$`no of persons`)])

ggplot(data = Scores_bd, aes( x = Scores, y = `no of persons`, fill =`no of persons`) )+  geom_bar( stat = "identity", color="cyan")  + ggtitle("Plot of Scores vs Frequency")
       
```

The performance is encouraging. As More than half of the participating students have scored more than 15 (way above the half mark). 



# Histogram plot 

```{r score distribution}

ggplot(data = file, aes( x = Scores) )+ 
  
  geom_histogram(color = "black", fill = "steelblue", binwidth = 0.9)  + ggtitle("Histogram plot of scores") + labs(x = "Scores", y = "Frequency")+  theme_minimal()
  

```

This is the distribution of the scores. The scores are skewed to the left. This is a pointer that the scores of the participating students are densely populated in the range 15 - 20 interval.  Only a handful of persons have scored 10 & 5
